%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\newcommand{\jobtitle}[1]{\runsubsection{\normalsize{#1}}}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Martin}{Miguel}{ % Your name
\urlstyle{same}\url{http://liaa.dc.uba.ar} \\ % Your website, LinkedIn profile or other web address
\href{mailto:mmiguel@dc.uba.ar}{mmiguel@dc.uba.ar} \\
+541131816018 \\
Yatay 50, C1184ACB, CABA, Buenos Aires, Argentina
}


%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\descript{PhD in Computer Science}
\location{Expected April 2021 - April 2016 | UBA, Buenos Aires, Argentina}
Advisor: Diego Fernandez Slezak - LIAA, DC, UBA, Buenos Aires, Argentina; ICC, CONICET-UBA, Argentina \\
Co-advisor: Mariano Sigman - LNI, UTDT, Buenos Aires, Argentina

\sectionspace

\descript{BS + MS in Computer Science}
\location{December 2015 - April 2008 | UBA, Buenos Aires, Argentina}

\sectionspace


%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\jobtitle{Assistant Professor}
\descript{| Universidad de buenos aires}
\location{Currently - April 2016}
Assistant Professor of \emph{Algorithms and Data Structures II}.

\sectionspace 

\jobtitle{Data Scientist}
\descript{| Avenida.com}
\location{March 2016 - January 2016}
Improvement of search engine configuration, implementation of
\emph{search-as-you-type} features and assistance in team management.

\sectionspace

\jobtitle{Software Engineer}
\descript{| MateMarote}
\location{December 2015 - April 2015}
Development of java backend infrastructure and javascript videogames for a
neuroscientifically based educational software.

\sectionspace

\jobtitle{Intern Software Engineer}\descript{| Google.com}
\location{April 2014 - January 2014}
Development and extensions of testing frameworks for
performance, end-to-end and regression tests.

\sectionspace

\jobtitle{Java Programmer}\descript{| Despegar.com}
\location{December 2013 - August 2012}
Development of components integrating a larger application system. Development
of web applications and utility frameworks.

\sectionspace

\jobtitle{Assistant Professor}\descript{| Universidad de Buenos Aires}
\location{July 2012 - March 2011}
Assistant Professor of \emph{Algorithms and Data Structures I \& II}.

\sectionspace

\jobtitle{Jr. Java Programmer (J2ME / Blackberry)}\descript{| SenseByte}
\location{January 2010 - January 2009}
Development of both stand-alone and client-server applications. Development of
applications interfacing with non-standard hardware.

\sectionspace



%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\subsection{Publications}

\descript{Mate Marote: a BigData platform for massive scale
educational interventions.}
\location{Martin A. Miguel}
45-JAIIO, 2016, Buenos Aires, Argentina (ISSN: 2451-7569).

\sectionspace

\descript{Inferencia de Tactus con Fundamentos Estadı́sticos para Tap-dancing.}
\location{Martin A. Miguel}
44-JAIIO, 2015, Rosario, Argentina (ISSN: 2451-7585).

\sectionspace

\descript{From beat tracking to beat expectation}
\location{Martin A. Miguel, Diego Fernandez Slezak, Mariano Sigman}
(Under review) Music Cognition

\sectionspace

\descript{In progress}
\location{Martin A. Miguel, Diego Fernandez Slezak, Mariano Sigman}
Paper describing an experimental setup for tapping used to measure
synchronization of responses against the stimuli. The setup requires minimal 
not-specialized equipment.

\descript{In progress}
\location{Martin A. Miguel, Diego Fernandez Slezak, Mariano Sigman}
Paper describing evaluation of beat expectation model against experimentally 
captured responses of tapping.

\sectionspace

\section{Scholarships}

\descript{PhD Grant | CONICET, Argentina}
\location{April 2021 - April 2016}

\sectionspace

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\input{transcript-en.tex}

\sectionspace % Some whitespace after the section



\end{document}
