%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\bil{
\cvsection{Main Publications}
}{
\cvsection{Publicaciones Principales}
}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%%---------------------------------------------------------
%\bil{
%\cvsubsection{Published}
%}{
%\cvsubsection{Publicadas}
%}
%%---------------------------------------------------------

\begin{cvpubs}

  \cvpub{Somacal, L., Riera, P., Fernandez Slezak, D. \textbf{Miguel, M. A.}
  \emph{Symbolic music style transfer via latent space transformations: model
  and evaluation} Latin American Music Information Retrieval Workshop, Rio de
  Janeiro, Brazil, December 2024 (In press)}{Conference paper on machine
  learning model for music style transfer in symbolic music}

  \cvpub{Cossavella, F., \textbf{Miguel, M.A}, Fernandez Slezak, D.
  \emph{The Role Of The Motor System In The Processing Of Rhythmic Complexity: A
  Critical Review}
CogSci 2024, Rotterdam, Netherlands, July 2024 (In press).}
{Conference paper reviewing fMRI studies reporting the relative activation of motor areas with respect to rhythmic complexity.}

  \cvpub{
		 Kiss L, Guiot C, Hashim S, D’Aleman Arango N, \textbf{Miguel MA}. (2022) The 14th
International Conference of Students of Systematic Musicology (SysMus21). Music
\& Science. doi:10.1177/20592043221076613.}{Conference report.}


  \cvpub{\textbf{Miguel, MA} and Fernandez Slezak, D. (2021) Modeling beat uncertainty as a 2D distribution of period and
phase: a MIR task proposal. Proc. of the 22nd Int. Society for Music Information
Retrieval Conf., Online.}{Paper describing a methodology to model beat uncertainty considering period
and phase from free tapping data and an evaluation criterion for MIR models.}

  \cvpub{Pironio N, Fernandez Slezak D, and \textbf{Miguel MA}. (2021) Pulse clarity metrics developed from a deep learning beat tracking
model. 
Proc. of the 22nd Int. Society for Music Information
Retrieval Conf., Online, 2021.}%
{Paper describing metrics of pulse clarity obtained from modifications to a
neural-network based beat tracking model. }

\cvpub{\textbf{Miguel MA}, Riera P, and Fernandez Slezak D. (2021) A simple and cheap setup for timing tapping responses synchronized
to auditory stimuli. Behav Res. https://doi.org/10.3758/s13428-021-01653-y
}{Paper describing an experimental setup for capturing timing of
tapping responses synchronized against auditory stimuli. The setup requires
minimal programming skills and uses unexpensive equipment.}

\cvpub{\textbf{Miguel MA}, Sigman M, and Fernandez Slezak D. (2020) From beat tracking to beat expectation: Cognitive-based beat
tracking for capturing pulse clarity through time. PLoS ONE 15(11): e0242207.
https://doi.org/10.1371/journal.pone.0242207}%
{Paper presenting a model of beat tracking adapted to produce a metric of
pulse-clarity over time.} 

\end{cvpubs}


% %---------------------------------------------------------
%\cvsubsection{In Review}
% %---------------------------------------------------------

%\begin{cvpubs}
%  \cvpub{Manuscript 1}{}
%
%  \cvpub{Manuscript 2}{}
%\end{cvpubs}

%% %---------------------------------------------------------
%\bil{
%\cvsubsection{In Prepreparation}
%}{
%\cvsubsection{En Preparación}
%}
%% %---------------------------------------------------------

%
%\begin{cvpubs}
%\small \color{black}
%\cvpub{Recuperación de Información Musical}
%{Contribution on chapter for onset detection, beat tracking and meter inference
%  in book in spanish providing a review on Music
%  Information Retrieval algorithms. 
%}
%
%\cvpub{Grammar-based modeling of rhythmic perception}
%{Paper describing a model of beat and meter expectation using grammar-based
%  bayesian inference.
%To be presented in \emph{Music Cognition Journal}.
%}
%
%\end{cvpubs}

% %---------------------------------------------------------
